---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
Load and process/transform
```{r}
```


## What is mean total number of steps taken per day?
Total Number Per Day
```{r}
```

Histogram
```{r}
```

Mean/Median Per Day
```{r}
```

## What is the average daily activity pattern?
Avg Steps Taken every 5 minutes over time
```{r}
```

5-Minute Interval with most steps
```{r}
```

## Imputing missing values
Total Missing Values
```{r}
```

Strategy to impute values
-
-

Dataset with Imputed Values
```{r}
```

Histogram total number of steps per day
```{r}
```

Mean/median number of steps per day
```{r}
```

Do these values differ from the estimates from the first part of the assignment?
-

What is the impact of imputing missing data on the estimates of the total daily number of steps?
-
-

## Are there differences in activity patterns between weekdays and weekends?
Add day type (weekend or weekday) to dataset
```{r}
```

Avg number of steps taken in 5-minute intervals over time, by day type (see README for example)
```{r}
```
